Tablas_Ms_ HabitatAves

### 2020-12-10 Ms_HabitatAves.Rmd
Arreglo Ms con presentacion Lab

### Introduction

@@

### Methodology

```{r}

@@

@@

ggplot(NewData, aes(y=Pred, x=Habitat)) + geom_col(aes(fill=Grado_modificacion ), position="dodge") +
  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Species richness")+
   geom_errorbar(aes(ymin=Pred-SE, ymax=Pred+SE), position = position_dodge2(width = 0.1, padding = 0.7))+
  facet_grid(Ambiente ~ Temporada) + xlab("Habitat of origin")

@@

```{r, results='hide'}
##### METAMDS: Non-metric Multidimensional scaling- NMDS

@@

```{r}
#Inv

@@

  # Ok, now extract appropriate terms from the adonis model Calculating AICc
  # using residual sum of squares (RSS or SSE) since I don't think that adonis
  # returns something I can use as a likelihood function... maximum likelihood
  # and MSE estimates are the same when distribution is gaussian See e.g.
  # https://www.jessicayung.com/mse-as-maximum-likelihood/;
  # https://towardsdatascience.com/probability-concepts-explained-maximum-likelihood-estimation-c7b4342fdbb1
  # So using RSS or MSE estimates is fine as long as the residuals are
  # Gaussian https://robjhyndman.com/hyndsight/aic/ If models have different
  # conditional likelihoods then AIC is not valid. However, comparing models
  # with different error distributions is ok (above link).

@@

  # based on https://en.wikipedia.org/wiki/Akaike_information_criterion;
  # https://www.statisticshowto.datasciencecentral.com/akaikes-information-criterion/ ;
  # https://www.researchgate.net/post/What_is_the_AIC_formula;
  # http://avesbiodiv.mncn.csic.es/estadistica/ejemploaic.pdf;
  # https://medium.com/better-programming/data-science-modeling-how-to-use-linear-regression-with-python-fdf6ca5481be

@@

```{r}
#Prim

@@

[General overview of this section]
In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on corrected bird presences, and analysed bird assembles in those environment.

[Provide background information and justification]
The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile). The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.

[Provide an overview of the procedure/method itself]
Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu]. To estimate species assembles for habitats, the vegan package [@Vegan] was used. 
Particular species were analized in a continuos environmental gradient using ocupancy probability from occupancy models also with DiversityOcuppancy package [@divoccu].

[Provide details about what was done and used and shows that care was taken]
Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1). 
Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019. Surveys were conducted randomly during sunrise and the three hours later for 10 minutes, registering species and behaviour.

[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]

In order to understand habitat use by birds, bird activities were counted by each habitat

Fit of environmental variables on species ordination was also tested.

[Describe what was done by referring to existing mehods in the literature]
To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.

[Provide more detailed information about the method and show that was a good choice]
Covariables of detection and occupation are describedd in table 1.

```{r}
#figura 1 con los 6 ambientes costeros estudiados
```

1. Revisting the research aim/existing research
Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.

2. General overview of results
The six coastal urban habitats shows distingible birs species assembles where only a few species contribute to the difference between them. For these habitats, bird assemblages differ between winter and spring seasons.
Environmental variables can be responsible of both community identities and use of habitat idiviualy

Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla 3). Distribution of sites in graphical NMDS (Fig. \@ref(fig:NMDS)) showedthat both seassons presented differences in abundance of species mostly in the inland sites. Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.

```{r, results='hide'}
## test: ANOSIM

@@

Both sampled seasons showed that few species contribute to differences between habitats. Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.  (For a complete species list of SIMPER, see Suplementary material).

@@

```{r, fig.width=13, fig.height=6}

@@

```{r}
#ORDISTEP

#Invierno
#Step: AvesInv2 ~ AMBIENTE + Cultivos + `Plantacion de arboles`

#Primavera
#Step: AvesPrim2 ~ AMBIENTE + `Bosque nativo`

@@

```{r Comportamineto, fig.height=8, fig.width=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")

P <-ggplot(ComportamientoPrim) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

layout <- "
AAAAAAAA
BBBBBBB#
"
I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')

>>>>

# Introduction

@@

# Methodology

[General overview of this section]

In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition and analised occupancy of key species in those environments.

[Provide background information and justification]

The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile). The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that grew from a rural beach to a one of place of mayor urban growth in the las txx years.

[Provide an overview of the procedure/method itself]

Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu]. To estimate species assembles for habitats, the vegan package [@Vegan] was used. 
Particular species were analized in a continuos environmental gradient using ocupancy probability from occupancy models also with DiversityOcuppancy package [@divoccu].

[Provide details about what was done and used and shows that care was taken]
Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: natural rocky shore, modified rocky shore, natural beach, and urbanized beach, green area, and urban center (Fig. \@ref(fig:Ambientes)). 
Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019. Between four and six surveys were conducted daily randomly during sunrise and the three hours later for 10 minutes in each site. All species that were seen and heard were recorded.

[Continuing to describe what was done in detail, using language which comunicate that care was taken]

In order to understand habitat use by birds, environmental variables were prepared from landcover layers.
A 2000m diameter buffer was made

Environmental variables used by bird assembles were tested with a permanova for each season of sampling

```{r Ambientes, fig.cap="The six environments selected to sample: Natural rocky shore, modified rocky shore, natural beach, modified beach, green area, and urban center."}
#figura 1 con los 6 ambientes costeros estudiados

include_graphics("Ambientes_Aves.png")
```

[Describe what was done by referring to existing mehods in the literature]

To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.

[Provide more detailed information about the method and show that was a good choice]
Covariables of detection and occupation are describedd in table 1.
Ocupancy models were proyected to the study area.

1. Revisting the research aim/existing research

Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.

2. General overview of results

Species richnes is similar between same natural and modified environments. 
There are distingible birs species assembles where only a few species contribute to the difference between them. For these habitats, bird assemblages differ between winter and spring seasons.
Environmental variables can be responsible of both community identities and use of habitat individualy

```{r PredRiqueza}

@@

AvesInv_riq <- readRDS("AvesInv_riq.rds")
AvesPrim_riq <- readRDS("AvesPrim_riq.rds")

@@

ggplot(NewData, aes(y=Pred, x=Habitat)) + geom_col(aes(fill=Grado_modificacion ), position="dodge") +
  scale_fill_manual(name="Intervention", aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Species richness")+
   geom_errorbar(aes(ymin=Pred-SE, ymax=Pred+SE), position = position_dodge2(width = 0.1, padding = 0.7))+
  facet_grid(Ambiente ~ Temporada) + xlab("Habitat of origin")

@@

Species richnes is similar between two seasons of sampling, environments, nor habitat of origin of species. Althogh modified anvironmnet have less species for site, only urban centers are distinct.

```{r DataNMDS, results='hide'}
##### METAMDS: Non-metric Multidimensional scaling- NMDS

@@

Corrected abundances by detection probability

Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla ModGLMEstacion). Distribution of sites in graphical NMDS (Fig. \@ref(fig:NMDS)) showed that both seassons presented differences in abundance of species mostly in the inland sites. Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.

```{r DataAnosim, results='hide'}
## test: ANOSIM

```{r DataPermInv}
#Inv

@@

@@

@@

```{r DataPermPrim}
#Prim

@@

Altitud, oceano y cob veg en invierno
Altitud, oceano y sup imp en primavera

@@

Both sampled seasons showed that few species contribute to differences between habitats. Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.  (For a complete species list of SIMPER, see Suplementary material SimperPrim, SimperInv).

@@

```{r Ocupancia, fig.width=13, fig.height=6}

@@

@@

```{r Comportamiento, fig.height=8, fig.width=10}
# ComportamientoInv <- read_rds("ComportamientoInv.rds")
# I <-ggplot(ComportamientoInv) + 
#   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
#   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
#   scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
# 
# ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
# 
# P <-ggplot(ComportamientoPrim) + 
#   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
#   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
#   scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
# 
# layout <- "
# AAAAAAAA
# BBBBBBB#
# "
# I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
#

### 2020-12-10 README.Rmd
Arreglo Ms con presentacion Lab

Escritura de manuscrito en ingles **Ms_HabitatAves.Rmd**
El manuscrito cuenta con imput desde: 
- Algunos analisis ubicados en **Analisis_HabitatAves.R**. 
- Ocupancia de las especies obtenidas de simper para invierno y primavera en **Occu_especifica_Ms.R**, resultados en **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**.
- En la segunda parte del script **Occu_especifica_Ms.R** se encuentra las predicciones realizadas para las especies seleccionadas antariormente, utilizando la capa **Capas_Proporcion_small.rds** creada desde los buffers y la altura. Cada especie (8 de invierno y6 de primavera) tienen sus resultados exportados por separado **PredEstacionX_EspecieX.rds**
- graficos de comportamiento desde archivo **Comportamineto_Aves.R**, con abundancia corregida de invierno de **AbundInv_Corregido.rds** y **AbundPrim_Corregido.rds**

>>>>

Escritura de manuscrito en ingles **Ms_HabitatAves.Rmd**

El manuscrito cuenta con imput desde: 
- Algunos analisis ubicados en **Analisis_HabitatAves.R**. 
- Ocupancia de las especies obtenidas de simper para invierno y primavera en **Occu_especifica_Ms.R**, resultados en **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**.
- En la segunda parte del script **Occu_especifica_Ms.R** se encuentra las predicciones realizadas para las especies seleccionadas antariormente, utilizando la capa **Capas_Proporcion_small.rds** creada desde los buffers y la altura. Cada especie (8 de invierno y6 de primavera) tienen sus resultados exportados por separado **PredEstacionX_EspecieX.rds**
- graficos de comportamiento desde archivo **Comportamineto_Aves.R**, con abundancia corregida de invierno de **AbundInv_Corregido.rds** y **AbundPrim_Corregido.rds**

## Figuras para presentacion de laboratorio viernes 4 diciembre

Esta presentación surgió con la idea de darle una vuelta a los resultados de este estudio
Archivo: **Figuras presentacion lab.R**
Se alimenta de los archivos
- **RiquezaAves_ambiente.R** tiene riqueza de aves y la riqueza a partir de los modelos de prediccion
- desde **RiquezaAves_ambiente.R** se exportan **AvesInv_riq.rds** y **AvesPrim_riq.rds**

## Inclusion de comentarios de la reunion de lab

- Figura prediccion de riqueza al comienzo de resultados en manuscrito y tabla de modelos. Obtenido de **Figuras presentacion lab.R**

### 2020-12-10 Tablas_Ms_HabitatAves.Rmd
Arreglo Ms con presentacion Lab

```{r}
# GLMmixto con variables aleatorias
library(MuMIn)

@@

```{r,results='asis'}
#Modelo 1= Abundancia ~ Estacion * Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0
DF_seasson <- tibble(Model= c("$Estacion \\times Especie + Ambiente+ \\frac{1}{Sitio}$", "$Especie + Ambiente + \\frac{1}{Sitio}$"), AIC= c(17716.1, 18241.0))

@@

```{r, results='asis'}
Inv_DF <-  read.csv("ResumenSimper_Inv2.csv") %>% as.data.frame() 
kable(Inv_DF, booktabs = T)

@@

```{r, results='asis'}
Prim_DF <-  read.csv("ResumenSimper_Prim2.csv") %>% as.data.frame()
kable(Prim_DF, booktabs = T)

@@

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23Na - 21.04Gr + 44.82Sa}$",
                               "$\\psi_{Ld} = e^{12.45}$", 
                               "$\\psi_{Lp} = e^{47.82 -5.09Al -231.04Gr + 5.74Oc + 	4.40Pa}$", 
                               "$\\psi_{Pt} = e^{104.91 -0.59Al +	6.56Na	-2.93Sh -18.98Sa}$", 
                               "$\\psi_{Pb} = e^{-82.05 + 12.46Cr -15.13Gr + 	1.38Oc}$"))

@@

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia","Coragyps atratus", "Larosterna inca", "Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Sephanoides sephaniodes", "Turdus falcklandii"), 
                   Equation= c("$\\psi_{Cl} = e^{-1.77 + 1.83Sa}$", 
                               "$\\psi_{Ca} = e^{7.57 -3.29Pa +	33.80Sa}$", 
                               "$\\psi_{Li} = e^{140.42 -2.38Al	-92.31Na -38.88Sa}$", 
                               "$\\psi_{Ld} = e^{2289.33}$",
                               "$\\psi_{Lm} = e^{190.57 + 2.73Ve -4.07Al -134.07Gr +	20.05Sa}$", 
                               "$\\psi_{Pt} = e^{172.98 -2.01Al	-50.93Na -165.09Gr +	2.47Oc}$", 
                               "$\\psi_{Ss} = e^{-106.91 + 1.64Ve +	7.14Al -43.91Na +	5.09Sh -24.45Tr}$", 
                               "$\\psi_{Tf} = e^{687.42 + 29.20Ve +	48.41Al -34.88Oc	-505.66Gs +	59.49Tr -4.94Pa +	283.63Sa -51.82Tr}$"))

>>>>

```{r ModPredRiqueza}
# GLMmixto con variables aleatorias
library(MuMIn)

@@

```{r ModGLMEstacion,results='asis'}
#Modelo 1= Abundancia ~ Estacion * Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0
DF_seasson <- tibble(Model= c("$Estacion \\times Especie + Ambiente+ \\frac{1}{Sitio}$", "$Especie + Ambiente + \\frac{1}{Sitio}$"), AIC= c(17716.1, 18241.0))

@@

```{r SimperInv, results='asis'}
Inv_DF <-  read.csv("ResumenSimper_Inv2.csv") %>% as.data.frame() 
kable(Inv_DF, booktabs = T)

@@

```{r SimperPrim, results='asis'}
Prim_DF <-  read.csv("ResumenSimper_Prim2.csv") %>% as.data.frame()
kable(Prim_DF, booktabs = T)

@@

```{r ModOcuPrim, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23Na - 21.04Gr + 44.82Sa}$",
                               "$\\psi_{Ld} = e^{12.45}$", 
                               "$\\psi_{Lp} = e^{47.82 -5.09Al -231.04Gr + 5.74Oc + 	4.40Pa}$", 
                               "$\\psi_{Pt} = e^{104.91 -0.59Al +	6.56Na	-2.93Sh -18.98Sa}$", 
                               "$\\psi_{Pb} = e^{-82.05 + 12.46Cr -15.13Gr + 	1.38Oc}$"))

@@

```{r ModOcuInv, results='asis'}
DF_occu <- tibble( Species= c("Columba livia","Coragyps atratus", "Larosterna inca", "Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Sephanoides sephaniodes", "Turdus falcklandii"), 
                   Equation= c("$\\psi_{Cl} = e^{-1.77 + 1.83Sa}$", 
                               "$\\psi_{Ca} = e^{7.57 -3.29Pa +	33.80Sa}$", 
                               "$\\psi_{Li} = e^{140.42 -2.38Al	-92.31Na -38.88Sa}$", 
                               "$\\psi_{Ld} = e^{2289.33}$",
                               "$\\psi_{Lm} = e^{190.57 + 2.73Ve -4.07Al -134.07Gr +	20.05Sa}$", 
                               "$\\psi_{Pt} = e^{172.98 -2.01Al	-50.93Na -165.09Gr +	2.47Oc}$", 
                               "$\\psi_{Ss} = e^{-106.91 + 1.64Ve +	7.14Al -43.91Na +	5.09Sh -24.45Tr}$", 
                               "$\\psi_{Tf} = e^{687.42 + 29.20Ve +	48.41Al -34.88Oc	-505.66Gs +	59.49Tr -4.94Pa +	283.63Sa -51.82Tr}$"))
